Finding a closest point in a lattice of Voronoi's first kind

### 2014-07-27 reviews/response.tex

\end{itemize}

\begin{enumerate}

\item\textbf{Comment:} 
I believe Proposition 2.1 and 2.2 appear essentially verbatim in [8]. Same for Propositions
3.1 (which is essentially by definition) and 3.2, they appear in [9]. I don’t think it adds any
readability/anything of value to reprove them here.
\\\textbf{Response:}

We agree that these propositions are well known/straightforward, but would prefer to keep them. %We do not know of references to specific proofs that we can give for these (unlike Theorem~4.1 for which a proof is directly given in \cite[Theorem~3]{ConwaySloane1992_voronoi_lattice_3d_obtuse_superbases}).  
The proof of Proposition 2.1 has been shortened in response to comment~\ref{com:rev2halfopen} of reviewer 2 and the proof of Proposition 2.2 has also been shortened.  %A result like Proposition 2.2 does appear informally in~\cite[Sec~5]{Shalvi_iterativeslicer_2009}.  It would also be possible to instead used Micciancio and Voulgaris~\cite[Lemma~3.7]{MicciancioVoulgaris_deterministic_jv_2013}%As far as we are aware, the remarkable algorithm in~\cite{MicciancioVoulgaris_deterministic_jv_2013} does not rely upon bounding the number of lattice points inside a sphere (or any other volume).  Instead, the procedure operates recursively on scaled versions of the lattice.  The scaling is chosen to ensure that the target point always lies inside twice the Voronoi cell.

@@

%BLERG: Check that Theorems 2 and 3 in the published version of\cite{ConwaySloane1992_voronoi_lattice_3d_obtuse_superbases} are what I think they are!

\item\textbf{Comment:}  
page 8, lemma 5.1. I think you forgot a factor 2 preceding the double summations over S and T (at end of lemma statement, and also in the proof.) 
\\\textbf{Response:}
This error has been fixed.

\item\textbf{Comment:}  
page 11, ``with be'' $\to$ ``will be'' 
\\\textbf{Response:}
Fixed.

\item\textbf{Comment:}  
Displayed equation before ``Putting p=...'', a $|$ should be $\|$
\\\textbf{Response:}
Fixed.

### 2014-07-27 paper.tex
minor

\begin{theorem} \label{thm:revvecssuperbase} (Conway and Sloane~\cite[Theorem~3]{ConwaySloane1992_voronoi_lattice_3d_obtuse_superbases}) Let $\Lambda$ be a lattice of Voronoi's first kind with obtuse superbasis $b_1,\dots,b_{n+1}$.  The relevant vectors of $\Lambda$ are of the form,
\[
\sum_{i \in I} b_i
\]
where $I$ is a strict subset of $\{1, 2, \dots, n+1\}$ that is not empty, i.e., $I \subset \{1, 2, \dots, n+1\}$ and $I \neq \emptyset$.
\end{theorem}

>>>>

\begin{theorem} \label{thm:revvecssuperbase} \emph{(Conway and Sloane~\cite[Theorem~3]{ConwaySloane1992_voronoi_lattice_3d_obtuse_superbases})} Let $\Lambda$ be a lattice of Voronoi's first kind with obtuse superbasis $b_1,\dots,b_{n+1}$.  The relevant vectors of $\Lambda$ are of the form,
\[
\sum_{i \in I} b_i
\]
where $I$ is a strict subset of $\{1, 2, \dots, n+1\}$ that is not empty, i.e., $I \subset \{1, 2, \dots, n+1\}$ and $I \neq \emptyset$.
\end{theorem}
